\documentclass[margin, line]{res}

\usepackage{marvosym}
\usepackage{fontawesome}
\usepackage{hanging}
\usepackage{url}
\usepackage{hyperref}

\oddsidemargin -.5in
\evensidemargin -.5in
\textwidth=6.0in
\itemsep=0in
\parsep=0in
%if using pdflatex:
%\setlength{\pdfpagewidth}{\paperwidth}
%\setlength{\pdfpageheight}{\paperheight}

\hypersetup{
 colorlinks,%
 linkcolor=black,%
 citecolor=black,%
 filecolor=black,%
 urlcolor=black
}

\makeatletter
\newcommand{\rmnum}[1]{\romannumeral #1}
\newcommand{\Rmnum}[1]{\expandafter\@slowromancap\romannumeral #1@}
\makeatother

\newenvironment{list1}{
 \begin{list}{\ding{113}}{%
  \setlength{\itemsep}{0in}
  \setlength{\parsep}{0in} \setlength{\parskip}{0in}
  \setlength{\topsep}{0in} \setlength{\partopsep}{0in} 
  \setlength{\leftmargin}{0.17in}}}{\end{list}}
\newenvironment{list2}{
 \begin{list}{$\bullet$}{%
  \setlength{\itemsep}{0in}
  \setlength{\parsep}{0in} \setlength{\parskip}{0in}
  \setlength{\topsep}{0in} \setlength{\partopsep}{0in} 
  \setlength{\leftmargin}{0.2in}}}{\end{list}}


\begin{document}

\name{\Large Reto W\"{u}est \vspace*{.1in}}

\begin{resume}

\section{\sc Contact Information}

\vspace*{.05in}
\begin{tabular}{@{}p{4.435in}p{4.11in}}
Department of Political Science & \Mundus~\href{http://retowuest.net/}{http://retowuest.net}  \\
and International Relations     & \Letter~\href{mailto:reto.wuest@unige.ch}{reto.wuest@unige.ch} \\
University of Geneva            & \faTwitter~\href{http://twitter.com/retowuest}{@retowuest}   \\
40 Boulevard du Pont d'Arve     & \faGithub~\href{http://github.com/retowuest}{retowuest}      \\
CH-1211 Geneva                  &  \\
Switzerland                     &  \\
\end{tabular}


\section{\sc Research Interests}

Legislative behavior, political representation, quantitative methods, and formal modeling.


\section{\sc Education}

\textbf{University of Geneva}, Switzerland \\
\vspace*{-.12in}
\begin{list1}
\item[] PhD in Political Science, 08/2016
\begin{list2}
\vspace*{.04in}
\item[] Dissertation title: ``Roll Call Votes in Democratic Legislatures: The Reasons for Their Use and Their Effects on Legislative Behavior''
\vspace*{.04in}
\item[] Advisor: Simon Hug
\vspace*{.04in}
\item[] Committee: Simon Hug, Scott Desposato, Nolan McCarty, and Jonas Pontusson
\end{list2}
\end{list1}

\textbf{New York University}, Department of Politics, USA \\
\vspace*{-.12in}
\begin{list1}
\item[] Visiting Scholar, 9/2014-8/2015
\begin{list2}
\vspace*{.04in}
\item[] Sponsor: David Stasavage
\end{list2}
\end{list1}

\textbf{Princeton University}, Department of Politics, USA \\
\vspace*{-.12in}
\begin{list1}
\item[] Visiting Student Research Collaborator (VSRC), 9/2013-8/2014
\begin{list2}
\vspace*{.04in}
\item[] Sponsor: Nolan McCarty
\end{list2}
\end{list1}

\textbf{University of Bern}, Switzerland \\
\vspace*{-.12in}
\begin{list1}
\item[] Lic.rer.soc. in Political Science (major) and Economics (minor), 10/2009
\end{list1}


\section{\sc Academic Positions}

\textbf{University of Geneva}, Department of Political Science and International Relations, Switzerland \\
\vspace*{-.12in}
\begin{list1}
\item[] Postdoctoral Researcher, since 09/2016
\vspace*{.04in}
\item[] Research and Teaching Assistant, 9/2015-08/2016
\vspace*{.04in}
\item[] Research Assistant, 8/2010-8/2013
\end{list1}

\textbf{University of Bern}, Center of Competence for Public Management, Switzerland \\
\vspace*{-.12in}
\begin{list1}
\item[] Research and Teaching Assistant, 1/2010-7/2010
\end{list1}

\textbf{University of Bern}, Institute of Political Science, Switzerland \\
\vspace*{-.12in}
\begin{list1}
\item[] Research Assistant, 11/2009-12/2009
\vspace*{.04in}
\item[] Undergraduate Research and Teaching Assistant, 8/2007-10/2009
\end{list1}


\section{\sc Additional Education}

\textbf{ICPSR Summer Program}, University of Michigan, USA \\
\vspace*{-.12in}
\begin{list1}
\item[] Advanced Game Theory, 7/2012-8/2012
\vspace*{.04in}
\item[] Matrix Algebra, 7/2012-8/2012
\vspace*{.04in}
\item[] Maximum Likelihood Estimation for Generalized Linear Models, 6/2011-7/2011
\vspace*{.04in}
\item[] Introduction to Game Theory, 6/2011-7/2011
\vspace*{.04in}
\item[] Introduction to the R Statistical Computing Environment, 6/2011-7/2011
\end{list1}

\textbf{CUSO Doctoral School in Political Science}, Switzerland \\
\vspace*{-.12in}
\begin{list1}
\item[] Rational Choice Theory, 2/2012
\vspace*{.04in}
\item[] Basic and Advanced Statistics, 2/2011
\end{list1}

\textbf{Summer School in Social Science Data Analysis}, University of Essex, UK \\
\vspace*{-.12in}
\begin{list1}
\item[] Empirical Models of Context Conditionality, (Inter)Dependence and Endogeneity, 8/2009
\vspace*{.04in}
\item[] Pooled Time Series Cross-Sectional Analysis, 8/2008
\end{list1}

\textbf{University of Zurich}, Switzerland \\
\vspace*{-.12in}
\begin{list1}
\item[] Swiss mobility program, Spring 2007
\end{list1}

\textbf{Lund University}, Sweden \\
\vspace*{-.12in}
\begin{list1}
\item[] Visiting student (Erasmus exchange program), Fall 2006
\end{list1}


\section{\sc Peer-Reviewed Articles}

\begin{hangparas}{0.17in}{1}
Lloren, Anouk and Reto W\"{u}est. 2016. ``Are Opinion Leaders Better Represented?'' \textit{West European Politics} 39(4):800-834.
\end{hangparas}

\vspace{-2mm}
\begin{hangparas}{0.17in}{1}
Hug, Simon, Simone Wegmann and Reto W\"{u}est. 2015. ``Parliamentary Voting Procedures in Comparison.'' \textit{West European Politics} 38(5):940-968.
\end{hangparas}

\vspace{-2mm}
\begin{hangparas}{0.17in}{1}
Lloren, Anouk, Jan Rosset and Reto W\"{u}est. 2015. ``Descriptive and Substantive Representation of Poor Citizens in Switzerland.'' \textit{Swiss Political Science Review} 21(2):254-260.
\end{hangparas}


\section{\sc Articles Under Review}

``Technocracy or Democracy? European Citizens' Perceptions of Expert Rule'' \\
(with Tina Freyburg, Ivo Krizic, and Sandra Lavenex)


\section{\sc Working Papers}

``Do Citizens Prefer Affluent Representatives? Evidence from a Survey Experiment in Switzerland'' \\
(with Jonas Pontusson)

\vspace{-2mm}
``Improving Multilevel Regression with Post-Stratification Through Optimal Model Selection'' \\
(with Philipp Broniecki and Lucas Leemann)

\vspace{-2mm}
``Legislator Income and Voting Behavior'' \\
(with Jan Rosset)

\vspace{-2mm}
``Party Pressure in Roll Call Votes'' \\
(with Simon Hug)

\vspace{-2mm}
``Who Represents the Poor? Evidence from Swiss Direct Democracy'' \\
(with Anouk Lloren)

\vspace{-2mm}
``Ideological Positions of Party Switchers'' \\
(with Simon Hug)


\section{\sc Book Project}

``Media Driven Accountability: The Role of Mass Media for the Monitoring of Governance'' \\
(with Michael Amsler, Chris Ewert, Jofre Rocabert, Michael Strebel, and Bruno W\"{u}est)


\section{\sc Media}

\begin{hangparas}{0.17in}{1}
Hug, Simon, Simone Wegmann and Reto W\"{u}est. 2012. ``Der St\"{a}nderat wird zum europ\"{a}ischen Normalfall'', \textit{Neue Z{\"u}rcher Zeitung} No. 183.
\end{hangparas}

\vspace{-2mm}
\begin{hangparas}{0.17in}{1}
Hug, Simon, Simone Wegmann and Reto W\"{u}est. 2012. ``Pourquoi le Conseil des Etats persiste-t-il \`{a} voter \`{a} main lev\'{e}e?'' \textit{Le Temps} 08 juin.
\end{hangparas}

\vspace{-2mm}
\begin{hangparas}{0.17in}{1}
Hug, Simon and Reto W\"{u}est. 2011. ``Achsen des Unsinns'', \textit{Die Weltwoche} No. 45.11.
\end{hangparas}

\vspace{-2mm}
\begin{hangparas}{0.17in}{1}
Hug, Simon and Reto W\"{u}est. 2011. ``Von Torten, Parlamentarier-Ratings, und anderen Ungeniessbarkeiten: Eine Nachlese zu den Wahlen 2011'', \textit{PoliSciZurich: A blog by political Scientists in Zurich}.
\end{hangparas}


\section{\sc Conference Participation}

APSA (2016, 2017, 2018)

\vspace{-3mm}
MPSA (2012, 2013, 2014, 2015)

\vspace{-3mm}
EPSA (2012, 2013, 2014, 2015, 2016, 2017, 2018)

\vspace{-3mm}
SPSA (2013, 2017, 2018)

\vspace{-3mm}
ECPR Standing Group on Parliaments (2012, 2014, 2017)

\vspace{-3mm}
NCCR Democracy Internal Conference (2016, 2017)

\vspace{-3mm}
International Conference of Europeanists (2014)

\vspace{-3mm}
ECPR Joint Sessions of Workshops (2011)


\section{\sc Invited Presentations}

\textbf{University of Geneva}, Unequal Democracies Seminar (2018)

\vspace{-3mm}
\textbf{University of Zurich}, Department of Political Science (2017)

\vspace{-3mm}
\textbf{Princeton University}, CSDP (2015)

\vspace{-3mm}
\textbf{University of Geneva}, UNIGE-Princeton University Workshop (2014)

\vspace{-3mm}
\textbf{ETH Zurich}, CIS (2011, 2012, 2013)


\section{\sc Research Grants}

Swiss National Science Foundation, Project ``Why are poor citizens underrepresented in parliament?'' (with Jonas Pontusson), CHF $282{,}500$ (2016)


\section{\sc Personal Grants}

Swiss National Science Foundation, Doc.Mobility Funding of Conference Costs, CHF $1{,}000$ (2015)

\vspace{-3mm}
Swiss National Science Foundation, Doc.Mobility fellowship, USD $46{,}300$ (2014)

\vspace{-3mm}
Fondation Ernst et Lucie Schmidheiny, Mobility fellowship, CHF $30{,}000$ (2013)

\vspace{-3mm}
Swiss Academy of Humanities and Social Sciences, Conference Travel Grant, CHF $1{,}200$ (2013)

\vspace{-3mm}
Swiss National Science Foundation, Summer School Travel Grant, CHF $4{,}400$ (2012)


\section{\sc Awards}

Prix Universal for the best PhD thesis in the Geneva School of Social Sciences in 2016, CHF $2{,}000$


\section{\sc Teaching}

\textbf{Pompeu Fabra University}, RECSM Summer School in Survey Methodology, Spain \\
\vspace*{-.12in}
\begin{list1}
\item[] ``Machine Learning for Social Sciences,'' 2018
\end{list1}

\textbf{University of Geneva}, Global Studies Institute, Switzerland \\
\vspace*{-.12in}
\begin{list1}
\item[] ``International Cooperation and Conflict,'' BA class, Spring 2016
\end{list1}

\textbf{University of Bern}, Center of Competence for Public Management, Switzerland \\
\vspace*{-.12in}
\begin{list1}
\item[] ``Empirical Research Methods'' (with Fritz Sager and Eva Thomann), MA class, Spring 2012
\vspace*{.04in}
\item[] ``Empirical Research Methods'' (with Fritz Sager and Eva Thomann), MA class, Spring 2011
\vspace*{.04in}
\item[] ``Empirical Research Methods'' (with Fritz Sager and Christine Zollinger), MA class, Spring 2010
\vspace*{-.13in}
\item[] ``Introduction to Statistics with Stata,'' Executive MPA, 1/2010
\end{list1}


\section{\sc Teaching Assistant}

\textbf{University of Bern}, Institute of Political Science, Switzerland \\
\vspace*{-.12in}
\begin{list1}
\item[] ``Empirical Research Methods,'' BA class, Spring 2009
\vspace*{.04in}
\item[] ``Introduction to Political Science,'' BA class, Fall 2008
\end{list1}


\section{\sc Work \\Experience}

\textbf{Federal Statistical Office}, Education System and Science, Neuch\^atel, Switzerland \\
\vspace*{-.12in}
\begin{list1}
\item[] Internship, 3/2008-8/2008
\end{list1}


\section{\sc Computer Skills}

\textbf{Data Analysis} \\
\vspace*{-.12in}
\begin{list1}
\item[] R, Stan, JAGS, Python, Stata, EViews, and MATLAB
\end{list1}

\textbf{Web Development} \\
\vspace*{-.12in}
\begin{list1}
\item[] HTML, CSS, PHP, and Markdown
\end{list1}


\section{\sc Languages}

English (fluent), German (native), French (basics)


\section{\sc Professional Service}

\textbf{Reviewer} \\
\vspace*{-.12in}
\begin{list1}
\item[] \textit{American Journal of Political Science}, \textit{British Journal of Political Science}, \textit{Political Science Research and Methods}, \textit{West European Politics}, \textit{European Policy Analysis}, \textit{Studies in Communication Sciences}
\end{list1}


\section{\sc References}

Available upon request


\vspace{4mm}

\begin{flushright}
\begin{small}
\textit{Last updated: \today}
\end{small}
\end{flushright}


\end{resume}
\end{document}
